Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
review error handl

%%What she said
Following the discussions in the interview, it became clear that the error handling was indeed changed but not for the reasons we assumed. A reason given was that the previous error handling implementations lacked information and usability. Glib, a common C library was also introduced to the new API. The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API. However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.

>>>>

%%What she said
During the interview, it was made clear that the previous error handling implementations lacked information and usability. Glib, a common C library was also introduced to the new API. The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API. However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
